Red Oak: Something Something Algorithmic Policy

### 2015-05-08 draft.tex
lstlisting keyword for api

@@

\begin{figure}[ht]
\begin{lstlisting}
f(pkt):
  if in_range(pkt, src, 0, 10) then
     if in_range pkt dst  [(0,10)] then
        deliver
     else 
        add pkt (IpDst, IpSrc) ``conn'';
        deliver
  else if in_rel pkt (IpSrc,IpDst) ``conn'' then
         deliver
       else
         drop
       end
  end                
  \end{lstlisting}

@@

In Figure~\ref{fig:rel_api}, we include the relation portion of the \lstinline|A.P.I.|, used to model stateful controller programs. A \lstinline|relation| represents a table in which each row contains a series of field values. It is referred to by a string. Policy writer may add a row to a relation \lstinline|rel| by calling the function \lstinline|add pkt flds rel|, which will populate the new row with the fields \lstinline|flds|' values of the current packet \lstinline|pkt|. Similarly, they may remove a row containing exactly the values of fields \lstinline|flds|' values of the current packet \lstinline|pkt| by calling \lstinline|remove pkt flds rel|. Finally, one may test if the values of fields \lstinline|flds| of current packet \lstinline|pkt| are in relation \lstinline|rel| by calling \lstinline|in_relation pkt flds rel|.

@@

val in_relation: packet -> field list -> relation -> bool
\end{lstlisting}

@@

\begin{figure}[ht]
  \begin{lstlisting}
(* compile a user-function into a policy *)
val compile: (packet -> forwarding_decision) -> policy

(* run the user-defined policy with a set of input packets *)
val run: policy -> ((field * int) list) list  -> unit

(* Print the policy to stdout *)
val print_policy: policy -> unit
  \end{lstlisting}

>>>>

\lstset{morekeywords={in_range, in_rel, add, remove, Drop, Deliver, ForwardTo, Multicast, IpSrc, IpDst}}

@@

\begin{figure}[ht]
\begin{lstlisting}
f(pkt):
  if in_range(pkt, src, 0, 10) then
     if in_range pkt dst  [(0,10)] then
        Deliver
     else 
        add pkt (IpDst, IpSrc) ``conn'';
        Deliver
  else if in_rel pkt (IpSrc,IpDst) ``conn'' then
         Deliver
       else
         Drop
       end
  end                
  \end{lstlisting}

@@

In Figure~\ref{fig:rel_api}, we include the relation portion of the \lstinline|A.P.I.|, used to model stateful controller programs. A \lstinline|relation| represents a table in which each row contains a series of field values. It is referred to by a string. Policy writer may add a row to a relation \lstinline|rel| by calling the function \lstinline|add pkt flds rel|, which will populate the new row with the fields \lstinline|flds|' values of the current packet \lstinline|pkt|. Similarly, they may remove a row containing exactly the values of fields \lstinline|flds|' values of the current packet \lstinline|pkt| by calling \lstinline|remove pkt flds rel|. Finally, one may test if the values of fields \lstinline|flds| of current packet \lstinline|pkt| are in relation \lstinline|rel| by calling \lstinline|in_rel pkt flds rel|.

@@

val in_rel: packet -> field list -> relation
    -> bool
\end{lstlisting}

@@

\begin{figure}[ht]
  \begin{lstlisting}
val compile: (packet -> forwarding_decision)
    -> policy

val run: policy -> ((field * int) list) list
    -> unit

val print_policy: policy -> unit
  \end{lstlisting}
